Realistically Interesting Domains for Probabilistic Planners

### 2014-04-07 FinalPaper/paper.tex
rewrote everything excepr gourmand

>>>>

\subsubsection{Traffic}

The traffic domain describes a crossroad with traffic lights, modelled as
cells. Either the north to south road has a green light, the west to east road
or all lights are red. The model uses a finite state machine that handles the
lights so that the lights are never green at the same time. This would be the
only dangerous situation on the crossroad. The difficulty in this domain is
the number of states, which grows exponentially with the number of cells.
Besides that it is an uninteresting probabilistic problem because it does
not satisfy the probabilistic interesting test.

\subsubsection{Elevators}
